Generate Frame Measures

### 2022-05-24 data-cleaning/07-generate-frame-measures.Rmd
indiv word cts

```{r}
box_write(case_frames,
           file_name = "case-level-frame-measures.csv",
           dir_id = 161199725595)
```

>>>>

```{r}
#box_write(case_frames,
#           file_name = "case-level-frame-measures.csv",
#           dir_id = 161199725595)
```

# Additional Info

```{r, eval=F}
frame = "women's_health"

phrases <- frame_terms %>% 
  filter(frame_code == frame) %>%
  select(word_clean) %>% 
  .[[1]]

# search tokens for the desired phrases, then create DFM
frame_freqs <- toks %>% 
  tokens_compound(pattern = phrase(phrases), concatenator = " ", 
                case_insensitive = FALSE, valuetype = "fixed") %>%
  tokens_select(phrases, case_insensitive = FALSE, valuetype = "fixed") %>%
  dfm()

# convert to df w/one row per brief+counts of phrases, joined w/brief info
frame_word_freqs <- frame_freqs %>% 
  convert(to = "data.frame") %>%
  left_join(amicus_info, by = "doc_id") %>% 
  select(case, id, brief, brief_party, word_ct, everything())

# add amicus author
amicus_type <- amicus %>% select(id, forgauf, legauf, legauo, lifauo,
                                 medauf, medauo, relauf, relauo)
frame_word_freqs <- frame_word_freqs %>% 
  left_join(., amicus_type, on = "id") %>% 
  select(-c(doc_id, legauf, legauo, lifauo, medauo, relauf, relauo)) %>% 
  select(case, brief, id, brief_party, forgauf, medauf, word_ct, sort(colnames(.)))

final <- frame_word_freqs %>% filter(forgauf == 1 | medauf == 1) %>% 
  mutate(case = str_replace(case, 'v\\.', 'v'),
         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""))

#xlsx::write.xlsx(final, file = "womens_health_cts.xlsx")
decisions <- readxl::read_xlsx("../eda/ab_cases.xlsx", sheet = "dat")
decisions <- decisions %>% 
  mutate(case = str_replace(case, 'v\\.', 'v'),
         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""),
         case = case_when(
           case == "Anders Solicitor of Richland County v Floyd" ~ "Anders v Floyd",
           case == "Ayotte AG of NH v Planned Parenhood of Northern New England" ~ "Ayotte v PP",
           case == "Beal Sec Dept of Public Wel of PA v Doe" ~ "Beal v Doe",
           case == "Bellotti Attorn Gen of MA v Baird 1979" ~ "Bellotti v Baird 1979",
           case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
           case == "Colautti Sec of Wel of PA v Franklin" ~ "Colautti v Franklin",
           case == "Doe et al v Bolton Attorn Gen of GA et al" ~ "Doe v Bolton",
           case == "Gonzales AG v Leroy Carhart" ~ "Gonzales v Carhart",
           case == "Gonzales v Planned Parenthood Federation of America" ~ "Gonzales v PP",
           case == "Harris Sec of HHS v McRae" ~ "Harris v McRae",
           case == "Hartigan Attor Gen of IL v David Zbaraz and Allan G Charles" ~ "Hartigan v Zbaraz",
           case == "Hill et al v Colorado" ~ "Hill v Colorado",
           case == "H L v Matheson Gov of UT" ~ "H.L. v Matheson",
           case == "Judy Madsen v Womens Health Center" ~ "Madsen v Womens Health Center",
           case == "Maher Comm of Soc Serv of CT v Roe" ~ "Maher v Roe",
           case == "NOW v Joseph Scheidler 1994" ~ "NOW v Scheidler 1994",
           case == "Ohio v Akron Center for Reproductive Health" ~ "Ohio v Akron Center",
           case == "Planned Parenthood Assoc of Kansas City MO v Ashcroft Attorn Gen of MO" ~
             "PP v Ashcroft",
           case == "Planned Parenhood of SE Penn v Casey" ~ "PP v Casey",
           case == "Planned Parenthood of Central MO v Danforth Attorn Gen of MO" ~ "PP v Danforth",
           case == "Roe et al v Wade District Attorn of Dallas County" ~ "Roe v Wade",
           case == "Rust v Sullivan Sec of HHS" ~ "Rust v Sullivan",
           case == "Joseph Scheidler v NOW 2003" ~ "Scheidler v NOW 2003",
           case == "Scheidler v NOW 2006" ~ "Scheidler v Now 2006",
           case == "Schenck et al v Pro-Choice Network of Western NY" ~
             "Schenck v Pro-Choice Network",
           case == "Stenberg AG of Neb v Leroy Carhart" ~ "Stenberg v Carhart",
           case == "Thornburgh Gov of PA v American College of Obstetricians and Gynecologists" ~
             "Thornburgh v American College of OBGYNs",
           case == "Webster Attor Gen of MO v Reproductive Health Services" ~ "Webster v Reproductive Health Services", 
           case == "Whole Womans Health v Hellerstedt" ~ "WWH v Hellerstedt",
           T ~ case
         )) %>%
  arrange(case)

final %>% 
  janitor::clean_names() %>% 
  left_join(., decisions, by = "case") %>% 
  mutate(death = mortality+morbidity) %>% 
  group_by(fem_win, forgauf, medauf) %>% 
  summarize(n = sum(death))

final %>% 
  janitor::clean_names() %>% 
  left_join(., decisions, by = "case") %>%
  mutate(death = mortality+morbidity) %>% 
  filter(forgauf == 1, fem_win == 0) %>% 
  group_by(case, ddate2) %>% 
  summarize(n = sum(death)) %>% 
  arrange(ddate2)

final %>% 
  janitor::clean_names() %>% 
  left_join(., decisions, by = "case") %>% 
  mutate(illegal_abortion = illegal_abortion+illegal_abortions,
         safe_abortion = safe_abortion + safe_legal_abortion,
         self_abortion = self_abortion+self_abortions+
           self_induced_abortion+self_induced_abortions) %>% 
  select(-id, -brief_party, -word_ct, -sentences, -tokens, -types) %>% 
  group_by(fem_win, forgauf, medauf) %>%
  #summarize(across(where(is.numeric), ~sum(.x)))
  summarize(illegal_abortion = sum(illegal_abortion),
            safe_abortion = sum(safe_abortion),
            self_abortion = sum(self_abortion))
```
